A Linked Open Social Database for Scientific Benchmarking

### 2016-08-03 paper.tex
pequena melhora na escrita da introp

% In recent years, the web of linked data~\cite{lee1} has attracted wide attention in
% both research and application realms.
Open machine-readable contents and tools are desired
in performing knowledge discovery in social data,
% there is a lack of datasets for benchmarking results,
However, there is a lack of datasets for benchmarking results,
specially associated the complex networks field,
yielding diverse results from poorly related sources.

The enormity of the digital data propels a rapid development of analysis methods
from different perspectives.
However, the used datasets in the literature differ within the scope of each research with
scarce and historical exceptions such as the
karate club dataset~\cite{newmanBook}.
On the other hand, the available linked data is not 
stable or rigorous enough to be
a public reference on statistical physics and social networks research.

This work presents a framework that provides machine-readable contents with a
database on social networks.
This has been made by linkng social data into an open social database with diverse
provenance, including Facebook, Twitter, IRC, Email and detached
instances.
Such data is proposed as a common repertoire for scientific
research involving networks and textual content and may be extended.

>>>>

% In recent years, the web of linked data~\cite{lee1} has attracted wide attention in
% both research and application realms.
Open machine-readable contents and tools are desired
in performing knowledge discovery in social data.
% there is a lack of datasets for benchmarking results,
However, there is a lack of open datasets for benchmarking results,
specially associated to the complex networks field,
yielding diverse results from poorly related sources.

The enormity of the digital data propels a rapid development of analysis methods
from different perspectives.
Even so, the used datasets in the literature differ within the scope of each research with
scarce and historical exceptions such as the
karate club dataset~\cite{newmanBook}.
Beyond that, the available linked data is not 
stable or rigorous enough to be
a public reference on statistical physics and social networks research.

This work presents a framework that provides machine-readable contents with a
database on social networks.
This has been made by linkng social data into an open database with diverse
provenance, including Facebook, Twitter, IRC, Email and detached
instances.
Such data is proposed as a common repertoire for scientific
research involving networks and textual content and may be extended.
